Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-03-22 tex/introduction/introduction.tex
restructure

\todo{fill in latest work}
In addition to those promising results, there is still work to do.
It still needs to be shown that the proposed workflow of statistical analysis of instance-level explanations can be successfully applied to other data types than binary feature vectors, such as numerical features or highly redundant features such as found in images.
Early results in this direction indicate that it might be beneficial to abandon the focus on features to explain machine learning models, but rather focus on instances directly.
That is using instance-level explanations to obtain groups of \emph{instances} with similar behavior and then visualize those groups (\eg, using techniques proposed by \cite{seekaview}) in order to \emph{implicitly} explain them.
This provides more flexible explanations than those proposed earlier as their capability goes beyond ``Feature A and feature B positively impact the prediction for this group of instances" to also allow insights of the form ``The number of circles formed by black pixels contribute positively to the prediction" which would be very difficult to formulate by a machine but are easily formulated by humans using visualizations.
Furthermore, we are going to run a study on the implications on confidence in and trust of machine learning models when using different explanation approaches.

The following document first describes the already completed stages: \infuse (\chapref{chap:infuse}), \prospector (\chapref{chap:prospector}), and the model diagnostic workflow using instance-level explanations (\chapref{chap:explainer}).
After that the progress on the current stage is described in \chapref{chap:current} and an outline for the thesis is given in \chapref{chap:thesis}.
%%%
%  Furthermore, a formalization or taxonomy of common machine learning modeling \emph{errors} in both the modeling and feature engineering steps is needed to fully determine the limitations of the proposed black-box analysis methodologies. This can be achieved by taking a survey with both machine learning and domain experts to get an understanding and relevance of different kinds of those errors.
%%%

>>>>

\todo{fill in latest work}
In addition to those promising results, there is still work to do.
It still needs to be shown that the proposed workflow of statistical analysis of instance-level explanations can be successfully applied to other data types than binary feature vectors, such as numerical features or highly redundant features such as found in images.
Early results in this direction indicate that it might be beneficial to abandon the focus on features to explain machine learning models, but rather focus on instances directly.
That is using instance-level explanations to obtain groups of \emph{instances} with similar behavior and then visualize those groups (\eg, using techniques proposed by \cite{seekaview}) in order to \emph{implicitly} explain them.
This provides more flexible explanations than those proposed earlier as their capability goes beyond ``Feature A and feature B positively impact the prediction for this group of instances" to also allow insights of the form ``The number of circles formed by black pixels contribute positively to the prediction" which would be very difficult to formulate by a machine but are easily formulated by humans using visualizations.
Furthermore, we are going to run a study on the implications on confidence in and trust of machine learning models when using different explanation approaches.
\todo{END?}

%%%
%  Furthermore, a formalization or taxonomy of common machine learning modeling \emph{errors} in both the modeling and feature engineering steps is needed to fully determine the limitations of the proposed black-box analysis methodologies. This can be achieved by taking a survey with both machine learning and domain experts to get an understanding and relevance of different kinds of those errors.
%%%

### 2018-03-22 tex/introduction/motivation.tex
restructure

@@

@@

>>>>

\begin{figure}
\centering
\includegraphics[height=6em,valign=t]{tex/introduction/pneumonia.png}
\includegraphics[height=8em,valign=t]{tex/introduction/age.png}
\includegraphics[height=8em,valign=t]{tex/introduction/asthma.png}
\caption{
\todo{TODO}
}
\label{figs:pneumonia}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/emradio.png}
\caption{
\todo{TODO}
}
\label{figs:emradio}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/adversarialtoaster.png}
\caption{
\todo{TODO}
}
\label{figs:toaster}
\end{figure}

### 2018-03-22 tex/introduction/usecase.tex
log reg and GAM
restructure

* Doctor decision tree (doctor note, limitations, residents vs. attending intuition; seniors might not be able to fully explain decisions made because of learned examples)
* inconsistent coding NDC, IDC, hierarchies

>>>>

* Doctor decision tree (doctor note, limitations, residents vs. attending intuition; seniors might not be able to fully explain decisions made because of learned examples)
* Bayesian reasoning / differential diagnosis
\todo{cite The Digital Doctor; Robert Wachter; Chapter 9}

\todo{outline -- summary of main contributions at the beginning of each chapter (Research Question: and Key Findings:)-- problem statement -- see anshuls thesis}
